TestEvol: A Tool for Analyzing Test-Suite Evolution

### 2012-11-03 icse2013demo-testevol/paper.tex
Added description about figures and new snapshots

Due to space limitations, we can only provide a few examples of
\tool's graphical interface. The companion video demonstration for
this paper illustrates the tool interface in full detail. Figure...

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{1-summary}
        \vspace*{-16pt}
	\caption{TBD.}
        \vspace*{-8pt}
	\label{fig:summary}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{2-versiondetails}
        \vspace*{-16pt}
	\caption{TBD.}
        \vspace*{-8pt}
	\label{fig:versiondetails}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{3-testdetails}
        \vspace*{-16pt}
	\caption{TBD.}
        \vspace*{-8pt}
	\label{fig:testdetails}
\end{figure}

>>>>

Due to space limitations, we can only provide a few examples of
\tool's graphical interface. The companion video demonstration for
this paper illustrates the tool interface in full detail. Figure~\ref{fig:summary}
shows the summary report generated by TestEvol. Such summary report
contains the total number of tests included in each one of the eight
categories we have defined in our approach, and previously described.
Note that beside the totals for all versions together, the summary also 
shows the results for each pair of versions. Figure~\ref{fig:versiondetails}
shows an example of the detailed report which shows details of all the tests
included in each one of the categories. In this figure is shown the list of
tests in the \catrep category. When tests in this category, and also those in
category \catref, are clicked, TestEvol opens a dialog which lets
the user compare two versions of the same test case. This is exemplified in Figure~\ref{fig:summary}.

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{1-summary}
        \vspace*{-16pt}
	\caption{Summary report generated from a \tool Analysis}
        \vspace*{-8pt}
	\label{fig:summary}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{2-versiondetails}
        \vspace*{-16pt}
	\caption{Detailed report for a pair of versions.}
        \vspace*{-8pt}
	\label{fig:versiondetails}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{3-testdetails}
        \vspace*{-16pt}
	\caption{Comparison between two different versions of a test case}
        \vspace*{-8pt}
	\label{fig:testdetails}
\end{figure}
